Alex's Notes and Text Fragments for the JOSS Manuscript

### 2021-04-22 paper/ABnotes.Rmd
added willmott reference

---
title: "Alex's Notes and Text Fragments for the JOSS Manuscript"
author: "Alexander Brenning"
date: "21 Apr 2021"
output: html_document
---

@@

*This is just a quick write-up, to be revised with more careful attention to referencing.*

@@

>>>>

---
title: "Alex's Notes and Text Fragments for the JOSS Manuscript"
author: "Alexander Brenning"
date: "21 Apr 2021"
output: html_document
bibliography: paper.bib
---

@@

@@

## References
